---
title: "Shiny Contest 2020: Interactive Presentation Ninja"
subtitle: "⚔<br/>with interactingan"
author: "Juan Cruz Rodriguez"
institute: "FAMAF - UNC"
date: "2020/03/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Start interacting!! [https://jcrodriguez.shinyapps.io/shiny_contest/](https://jcrodriguez.shinyapps.io/shiny_contest/)

```{r echo=FALSE, message=FALSE, fig.align='center'}
library("interactingan")
# Will configure an empty app to the shinyapps server;
# and show a qr code that points to the interactingan app url.
# Keep the resulting `shiny` app in the `out_dir` folder.
set_app(app_name = "shiny_contest", out_dir = "./resulting_shiny_app/")
```

---

# Which `shiny` app do you think is going to win the `shiny` contest?

`r interactingan::wordcloud("Shiny Contest 2020 winner", max_words = 1)`

---

# Have you already seen the `heyshiny` package?

`r poll("Already seen heyshiny?", c("Yes", "No", "Won't answer!"))`

---

# How likely would you use `interactingan`?

`r rating("Rate interactingan:")`

---

# Any feedback about `interactingan`?

`r question("Feedback:")`

---

# Questions?

<!-- Show the audience question's pane -->
`r audience_questions()`

```{r echo=FALSE}
# Deploys the final interactingan app to the shinyapps server
deploy_interactions()
```
